\mytitle{}

### 2018-07-10 paper/paper.tex
Way more content

%% IEEE CNS addition:
\makeatletter
\def\ps@headings{%
	\def\@oddhead{\mbox{}\scriptsize\rightmark \hfil \thepage}%
	\def\@evenhead{\scriptsize\thepage \hfil \leftmark\mbox{}}%
	\def\@oddfoot{}%
	\def\@evenfoot{}}
\makeatother
\pagestyle{empty}

@@

%% Fix indent in new section...
\newcommand{\subparagraph}{}
\usepackage{titlesec}
\titlespacing*{\section}{0pt}{1.5ex}{0.7ex}
%\titleformat*{\filcenter\scshape}

@@

\xpatchbibmacro{name:andothers}{%
	\bibstring{andothers}%
}{%
	\bibstring[\emph]{andothers}%
}{}{}

@@

\title{\mytitle{}}
\author{Kyle A. Simpson\thanks{This work was supported by the Engineering and Physical Sciences
		Research Council [grant number EP/M508056/1]}\\\emph{University of Glasgow, Glasgow, Scotland},\\
		\email{k.simpson.1@research.gla.ac.uk}}

@@

What is the story I'm trying to push?

?? Threat model yada yada everything sucks all the time here are some statistics about things being

@@

This paper contributes:
\begin{itemize}
	\item A DDoS mitigation system based on direct-control reinforcement learning designed for deployment in real-world software-defined networks.
	\item Important weaknesses and flaws in the past design and evaluation of similar techniques \cite{DBLP:journals/eaai/MalialisK15}---deconstruction of the ISP-like formulation, an acknowledgement of the flaws and risk factors of pushback \cite{DBLP:journals/ccr/MahajanBFIPS02a}.
	\item ?? TODO: Advancing the use/representation of state-space in direct-control RL of networked applications.
\end{itemize}

@@

%?? Introduce RL, related definitions etc.
\emph{Reinforcement learning} (RL) is a variant of machine learning principally concerned with with training an agent to perform optimally in the pursuit of a given task \cite{RL2E}.
We assume the agent has a certain amount of knowledge whenever a decision must be made: at any point in time $t$ it knows which \emph{state} it is in ($S_t \in \mathcal{S}$), the set of \emph{actions} which are available to it ($\mathcal{A} = A(S_t)$) and, if available, a numeric \emph{reward} obtained from the last action chosen ($R_t \in \mathbb{R}, A_t \in \mathcal{A}$).
RL methods combine this information with a \emph{policy} $\pi$ to determine which action should be taken: such a choice need not be optimal, if an agent needs to further explore some region of the state space.
The policy is then further refined by, for instance, updating value estimates for state-action pairs, meaning that RL-based approaches learn adaptively and online.
Formally, the goal is to maximise the \emph{expected discounted return}

?? Formalise?

?? Include some details of function approximation in the formalisation?

@@

?? Is this \emph{actually} just sarsa? We're using fn approx (of course), but this is fraught with its own difficulties. Is it strictly speaking correct to describe it as Sarsa at this point? It's, at the very least, 1-step semi-gradient Sarsa given that it is clearly on-policy...
?? IDEA: try out average reward, td($\lambda$) methods...

@@

\section{Methodology}

?? Either say ``I did it like \textcite{DBLP:journals/eaai/MalialisK15}, here are the differences (i.e., the \emph{real} innovations)'' or just spend time going over it again.

@@

\section{Performance in an emulated environment}

@@

?? TCP perf characteristics under packet drop known by the Mathis equation \cite{DBLP:journals/ccr/MathisSMO97}:
$$ \operatorname{BW} = \frac{\operatorname{MSS}}{\operatorname{RTT}} \frac{C}{\sqrt{p}},$$
for the \emph{maximum segment size} (MSS), \emph{round trip time} (RTT), a choice of constant $C \approx{} \sqrt{3/2}$ dependent on system assumptions and the probability $p \in (0, 1]$ that a packet is lost.
The lower bound on $p$ is deliberately open, as packet drop acts as a control signal for the TCP send window size.

@@

\section*{Acknowledgements}
My thanks go to Dr.\ Dimitrios Pezaros for his supervision, guidance, and comments relating to the realisation of this work.
Additional thanks \emph{would} go out to my anonymous reviewers, had I any of them.

>>>>

@@

%% Fix indent in new section...
\newcommand{\subparagraph}{}
\usepackage{titlesec}
\titlespacing*{\section}{0pt}{1.5ex}{0.7ex}
\titlespacing*{\subsection}{0pt}{1.5ex}{0.7ex}
%\titleformat*{\filcenter\scshape}

@@

\xpatchbibmacro{name:andothers}{%
	\bibstring{andothers}%
}{%
	\bibstring[\emph]{andothers}%
}{}{}
\DeclareFieldFormat[inproceedings]{url}{}
\DeclareFieldFormat[inproceedings]{article}{}

@@

\title{\mytitle{}}
\author{Kyle A. Simpson\thanks{This work was supported by the Engineering and Physical Sciences
		Research Council [grant number EP/M508056/1]}\\University of Glasgow, Glasgow, Scotland,\\
		\email{k.simpson.1@research.gla.ac.uk}}

@@

Network anomaly detection, intrusion detection and intrusion prevention are continually evolving problems, compounded by the partial, non-IID view of data at each point in the network.
Attacks and anomalous behaviours evolve, becoming more sophisticated or employing new vectors to harm a network or system's confidentiality, integrity, or availability without being detected.
These attacks and anomalies have measurable consequences and symptoms which allow a skilled analyst to infer new signatures for detection by misuse-based classifiers, but unseen attacks may only be defended against after-the-fact.

While \emph{machine learning} (ML) approaches seem like a sensible fit for this problem, in \citeyear{DBLP:conf/sp/SommerP10} \textcite{DBLP:conf/sp/SommerP10} identified the `failure to launch' of ML-based anomaly detection systems---to quite a large extent, this remains the case today.
Their application is made difficult due to significant operational differences from standard ML tasks, alongside certain characteristics of network traffic.
Briefly, these are the diversity of network traffic across varying timescales \cite{DBLP:conf/sp/SommerP10} and significant burstiness \cite{DBLP:journals/ccr/LelandWTW95}.
Above the aggregate level, the constant deployment of new services and new protocols means that traffic is \emph{non-stationary} and displays an evolving notion of normality.
This is compounded by the extraordinarily low tolerance for false positives inherent to network intrusion detection \cite{DBLP:conf/ccs/Axelsson99}, and the challenges of learning from unlabelled (often partial) data.
All of these factors greatly inflate the difficulty of the detection problem.

For certain classes of problem like non-transit DDoS attacks, \emph{reinforcement learning} (RL) is best-posed to adaptively react to certain classes of threat by assuming the role of a feedback loop for network optimisation, typically to safeguard service guarantees.
In a sense, this allows us to ``overcome'' the difficulties of the detection problem by monitoring \emph{performance characteristics and consequences} in real-time, by looking for the effect rather than the cause.
The intent is to augment what existing solutions can provide, by automatically alerting, recording and controlling what are believed to be illegal system states.
%Whether it takes direct control of the network, or is used indirectly to optimise a key part of another system, more powerful `deep' RL techniques (and well-founded action spaces) aren't yet well explored for network IDS/IPS.
%These range from more modern training algorithms \cite{DBLP:journals/corr/SchulmanWDRK17, DBLP:conf/icml/SchulmanLAJM15}, to evolutionary strategies \cite{DBLP:journals/corr/SalimansHCS17, DBLP:journals/corr/abs-1802-08842}, hierarchical action composition \cite{DBLP:journals/corr/abs-1710-09767}, and competitive multi-agent learning \cite{DBLP:journals/corr/abs-1710-03748}.

@@

This paper contributes:
\begin{itemize}
	\item A DDoS mitigation system based on direct-control reinforcement learning designed for deployment in real-world software-defined networks.
	\item Important weaknesses and flaws in the past design and evaluation of similar techniques \cite{DBLP:journals/eaai/MalialisK15}---a deconstruction of the ISP-like formulation, an acknowledgement of the flaws and risk factors of pushback \cite{DBLP:journals/ccr/MahajanBFIPS02a}.
	\item ?? TODO: Advance the use/representation/granularity of state-space in direct-control RL of networked applications.
\end{itemize}

@@

%?? Introduce RL, related definitions etc.
\emph{Reinforcement learning} (RL) is a variant of machine learning principally concerned with with training an agent to choose an optimal sequence of actions in the pursuit of a given task \cite{RL2E}.
We assume the agent has a certain amount of knowledge whenever a decision must be made: at any point in time $t$ it knows which \emph{state} it is in ($S_t \in \mathcal{S}$), the set of \emph{actions} which are available to it ($\mathcal{A} = A(S_t)$) and, if available, a numeric \emph{reward} obtained from the last action chosen ($R_t \in \mathbb{R}, A_t \in \mathcal{A}$).
RL methods combine this information with a current \emph{policy} $\pi$ to determine which action should be taken: such a choice need not be optimal, if an agent needs to further explore some region of the state space.
The policy is then further refined by updating value estimates for state-action pairs or via policy gradient methods, meaning that RL-based approaches learn adaptively and online if reward functions are available in their deployment environment.
From any point in a sequence of decisions, we may describe the sum of rewards yet to come as the \emph{return}, $G_t = R_{t+1} + \ldots + R_{t+T}$ for some (possibly infinite) choice of $T$.
Formally then, the goal is to maximise the \emph{expected return} $\operatorname{\mathbb{E}_{\pi}}[G_t | S_t]$ from any and all states $S_t$.

?? Include some details of function approximation in the formalisation? I.e. tile coding, stability and convergence guarantees...

@@

?? Is this \emph{actually} just sarsa? We're using fn approx (of course), but this is fraught with its own difficulties. Is it strictly speaking correct to describe it as Sarsa at this point? It's, at the very least, 1-step semi-gradient Sarsa given that it is clearly on-policy w/ fn approx...
?? IDEA: try out average reward, TD($\lambda$) methods as future work...

@@

\section{Environment and RL Algorithm}

@@

\subsection{Topology}
The network itself is tree-structured, where one server connects to $k$ team leaders, each connected to $l$ intermediate switches, which in turn each connect to $m$ egress switches.
Agents are co-located with these egress switches, who control the proportion of upstream packets from $n$ external hosts to discard according to load statistics observed along their path to the server.
Agents communicate with their co-hosted OpenFlow-enabled switches---running a modified version of \emph{Open vSwitch} (OVS) \cite{open-vswitch}---to install probabilistic packet-drop rules.

?? Diagram? TikZ?

Reimplementation of the network model was performed using mininet \cite{mininet}, a Python-based network emulator.
Traffic is played back from hosts via Tcpreplay at a bandwidth assigned uniformly from a `good' or `bad' distribution, each using the same pcap file with source and destination IP addresses rewritten.
While unrealistic with respect to packet content, it was assumed that this would provide representative load and packet inter-arrival characteristics.
A sufficiently well-trained agent needs only to follow the policy it has learned in a greedy manner, allowing pre-training using a priori knowledge by simulation to transfer to reality.

\subsection{Agent Definitions}

?? Specify update rules here? Sarsa \cite[pp.\ \numrange{129}{131}]{RL2E}? Semi-gradient Sarsa? enhanced by tile-coding with identical parameter choices \cite{DBLP:phd/ethos/Malialis14}.

?? Specify reward function here?

?? M\&K Seem not to have a grasp on the importance of up/down traffic splits. Hmm......... (i.e., both could be relevant?)

\section{Performance in an Emulated Environment}

?? System specs of execution environment: Intel Core i7-6700K clocked at \SI{4.2}{\giga\hertz}, with \SI{32}{\gibi\byte} of RAM. All code is available on a public Github repository\footnote{\url{https://github.com/FelixMcFelix/rln-dc-ddos-paper}}.

@@

?? TCP perf characteristics under packet drop known by the Mathis equation \cite{DBLP:journals/ccr/MathisSMO97}:
$$ \operatorname{BW} = \frac{\operatorname{MSS}}{\operatorname{RTT}} \frac{C}{\sqrt{p}},$$
for the \emph{maximum segment size} (MSS), \emph{round trip time} (RTT), a choice of constant $C \approx{} \sqrt{3/2}$ dependent on system assumptions and the probability $p \in (0, 1]$ that a packet is lost.
The lower bound on $p$ is deliberately open, as packet drop acts as a control signal for the TCP send window size and is an expected part of normal operation.

@@

?? Security? I suspect that the very qualities that make inference difficult in IDS/IPS also increase the level of challenge an advanced threat must overcome.
System state which is dependent on many signals drawn from across a wide network, in concert with their burstiness and unpredictability, may have substantial effects on an attacker's capabilities.

\section*{Acknowledgements}
My thanks go to Dr.\ Dimitrios Pezaros for his supervision, guidance, and comments relating to the realisation of this work, and to Mircea Iordache for his comments and technical assistance.
Additional thanks \emph{would} go out to my anonymous reviewers, had I any of them.
